Embracing the Laws of Physics: \\ Three Reversible Models of Computation

### 2018-06-22 survey/survey.tex
start explaining all of the level-2 Pi combinators.

\begin{figure}[t]
Let $c_1 : t_1 \leftrightarrow t_2$,  $c_2 : t_2 \leftrightarrow t_3$, and $c_3 : t_3 \leftrightarrow t_4$:
\[\def\arraystretch{1.3}
\begin{array}{c}
  {c_1 \odot (c_2 \odot c_3) \Leftrightarrow (c_1 \odot c_2) \odot c_3}
\\
  {(c_1 \oplus (c_2 \oplus c_3)) \odot \assoclp \Leftrightarrow \assoclp \odot ((c_1 \oplus c_2) \oplus c_3)}
\\
  {(c_1 \otimes (c_2 \otimes c_3)) \odot \assoclt \Leftrightarrow \assoclt \odot ((c_1 \otimes c_2) \otimes c_3)}
\\
  {((c_1 \oplus c_2) \oplus c_3) \odot \assocrp \Leftrightarrow \assocrp \odot (c_1 \oplus (c_2 \oplus c_3))}
\\
  {((c_1 \otimes c_2) \otimes c_3) \odot \assocrt \Leftrightarrow \assocrt \odot (c_1 \otimes (c_2 \otimes c_3))}
\\
  {\assocrp \odot \assocrp \Leftrightarrow ((\assocrp \oplus \idc) \odot \assocrp) \odot (\idc \oplus \assocrp)}
\\
  {\assocrt \odot \assocrt \Leftrightarrow ((\assocrt \otimes \idc) \odot \assocrt) \odot (\idc \otimes \assocrt)}
\end{array}\]
\caption{\label{figj}Signatures of level-2 $\Pi$-combinators: associativity}
\end{figure}

@@

@@

@@

But why are these particular coherence laws? Are they all necessary?
Conversely are they, in some appropriate sense, sufficient? This is
the so-called \emph{coherence problem}. Mac Lane, in his farewell address
as President of the American Mathematical Society~\cite{MacLane1976} gives
a good introduction and overview of such problems.  A more modern
interpretation (which can nevertheless be read into Mac Lane's own
exposition) would read as follows: given a set of equalities on abstract
words, regarded as a rewrite system, and two means of rewriting a word
in that language to another, is there some suitable notion of canonical
form that expresses the essential uniqueness of the non-trivial 
rewrites?  Note how this word-and-rewrite problem is essentially
independent of the eventual interpretation. One must take some care,
as there are obvious degenerate cases (involving ``trivial'' equations
involving $0$ or $1$) which lead to non-uniqueness. The landmark
results, first by Kelly-Mac Lane~\cite{KELLY197197} for closed
symmetric monoidal categories, then (independently) Laplaza and
Kelly~\cite{laplaza72,kelly74} for symmetric Rig Categories, is
that indeed there are sound and complete coherence conditions that
insure that all the ``obvious'' equalities between different abstract
words in these systems give rise to commutative diagrams. The
``obvious'' equalities come from \emph{syzygies} or
\emph{critical pairs} of the system of equations.

@@

The constructs in Fig.~\ref{figj} capture the informal idea that all
the different ways of associating programs are equivalent. For
example, a program that performs $c_1$ and then $(c_2 \odot c_3)$ can
be smoothly transformed a program that performs $(c_1 \odot c_2)$ and
then $c_3$. The last two equivalences show how several uses of
associativity interact together. For example, in the last equivalence
the program on the left $\assocrt \odot \assocrt$ transforms an input
type $((t_1 * t_2) * t_3) * t_4$ to an output type
$t_1 * (t_2 * (t_3 * t_4))$ as follows:

\begin{center}
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8}]
\node[above] (A) at (-2,0) {$t_1$}; 
\node[above] (B) at (-1.5,0) {$t_2$}; 
\node[above] (C) at (-1,0) {$t_3$}; 
\node[above] (D) at (-0.5,0) {$t_4$}; 
\draw[thick] (A) -- (-2,-1.5); 
\draw[thick] (B) -- (-1.5,-1.5); 
\draw[thick] (C) -- (-1,-1.5);; 
\draw[thick] (D) -- (-0.5,-1.5); 
\draw[red,densely dashed] (-1.75,-0.75) ellipse [x radius=0.4cm, y radius = 0.1cm];
\draw[green,densely dashed] (-1.6,-0.75) ellipse [x radius=0.85cm, y radius = 0.2cm];
\end{tikzpicture}
$\leadsto$ 
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8}]
\node[above] (A) at (-2,0) {$t_1$}; 
\node[above] (B) at (-1.5,0) {$t_2$}; 
\node[above] (C) at (-1,0) {$t_3$}; 
\node[above] (D) at (-0.5,0) {$t_4$}; 
\draw[thick] (A) -- (-2,-1.5); 
\draw[thick] (B) -- (-1.5,-1.5); 
\draw[thick] (C) -- (-1,-1.5);; 
\draw[thick] (D) -- (-0.5,-1.5); 
\draw[red,densely dashed] (-1.75,-0.75) ellipse [x radius=0.4cm, y radius = 0.1cm];
\draw[green,densely dashed] (-0.75,-0.75) ellipse [x radius=0.4cm, y radius = 0.1cm];
\end{tikzpicture}
$\leadsto$
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8}]
\node[above] (A) at (-2,0) {$t_1$}; 
\node[above] (B) at (-1.5,0) {$t_2$}; 
\node[above] (C) at (-1,0) {$t_3$}; 
\node[above] (D) at (-0.5,0) {$t_4$}; 
\draw[thick] (A) -- (-2,-1.5); 
\draw[thick] (B) -- (-1.5,-1.5); 
\draw[thick] (C) -- (-1,-1.5);; 
\draw[thick] (D) -- (-0.5,-1.5); 
\draw[red,densely dashed] (-0.9,-0.75) ellipse [x radius=0.85cm, y radius = 0.2cm];
\draw[green,densely dashed] (-0.75,-0.75) ellipse [x radius=0.4cm, y radius = 0.1cm];
\end{tikzpicture}
\end{center}
% \[ 
% ((t_1 * t_2) * t_3) * t_4 \leadsto
% (t_1 * t_2) * (t_3 * t_4) \leadsto
% t_1 * (t_2 * (t_3 * t_4))
% \]

\begin{center}
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8}]
\node[above] (A) at (-2,0) {$t_1$}; 
\node[above] (B) at (-1.5,0) {$t_2$}; 
\node[above] (C) at (-1,0) {$t_3$}; 
\node[above] (D) at (-0.5,0) {$t_4$}; 
\draw[thick] (A) -- (-2,-1.5); 
\draw[thick] (B) -- (-1.5,-1.5); 
\draw[thick] (C) -- (-1,-1.5);; 
\draw[thick] (D) -- (-0.5,-1.5); 
\draw[red,densely dashed] (-1.75,-0.75) ellipse [x radius=0.4cm, y radius = 0.1cm];
\draw[green,densely dashed] (-1.6,-0.75) ellipse [x radius=0.85cm, y radius = 0.2cm];
\end{tikzpicture}
$\leadsto$ 
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8}]
\node[above] (A) at (-2,0) {$t_1$}; 
\node[above] (B) at (-1.5,0) {$t_2$}; 
\node[above] (C) at (-1,0) {$t_3$}; 
\node[above] (D) at (-0.5,0) {$t_4$}; 
\draw[thick] (A) -- (-2,-1.5); 
\draw[thick] (B) -- (-1.5,-1.5); 
\draw[thick] (C) -- (-1,-1.5);; 
\draw[thick] (D) -- (-0.5,-1.5); 
\draw[red,densely dashed] (-1.25,-0.75) ellipse [x radius=0.4cm, y radius = 0.1cm];
\draw[green,densely dashed] (-1.5,-0.75) ellipse [x radius=0.85cm, y radius = 0.2cm];
\end{tikzpicture}
$\leadsto$
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8}]
\node[above] (A) at (-2,0) {$t_1$}; 
\node[above] (B) at (-1.5,0) {$t_2$}; 
\node[above] (C) at (-1,0) {$t_3$}; 
\node[above] (D) at (-0.5,0) {$t_4$}; 
\draw[thick] (A) -- (-2,-1.5); 
\draw[thick] (B) -- (-1.5,-1.5); 
\draw[thick] (C) -- (-1,-1.5);; 
\draw[thick] (D) -- (-0.5,-1.5); 
\draw[red,densely dashed] (-1.25,-0.75) ellipse [x radius=0.4cm, y radius = 0.1cm];
\draw[green,densely dashed] (-1.0,-0.75) ellipse [x radius=0.85cm, y radius = 0.2cm];
\end{tikzpicture}
$\leadsto$
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8}]
\node[above] (A) at (-2,0) {$t_1$}; 
\node[above] (B) at (-1.5,0) {$t_2$}; 
\node[above] (C) at (-1,0) {$t_3$}; 
\node[above] (D) at (-0.5,0) {$t_4$}; 
\draw[thick] (A) -- (-2,-1.5); 
\draw[thick] (B) -- (-1.5,-1.5); 
\draw[thick] (C) -- (-1,-1.5);; 
\draw[thick] (D) -- (-0.5,-1.5); 
\draw[green,densely dashed] (-0.9,-0.75) ellipse [x radius=0.85cm, y radius = 0.2cm];
\draw[red,densely dashed] (-0.75,-0.75) ellipse [x radius=0.4cm, y radius = 0.1cm];
\end{tikzpicture}
\end{center}
% \[
% ((t_1 * t_2) * t_3) * t_4 \leadsto
% (t_1 * (t_2 * t_3)) * t_4 \leadsto
% t_1 * ((t_2 * t_3) * t_4) \leadsto
% t_1 * (t_2 * (t_3 * t_4))
% \]

\noindent The equivalence states that these two sequences of steps can be
smoothly deformed to one another.

The constructs in Fig.~\ref{figi} explain how choice interacts with
grouping. Intuitively, a choice nested inside a larger bundle can also
be treated as an outer choice with the nested bundle duplicated in
each branch. 
\begin{center}
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8}]
\node[above] (A) at (-2,0) {$t_1$}; 
\node[above] (B) at (-1.5,0) {$t_3$}; 
\node[above] (C) at (-1,0) {$t_5$}; 
\draw[thick,yellow] (-1.5,-0.25) arc[start angle=60, end angle=120, radius=0.5cm];
\draw[thick] (A) -- (-2,-0.5); 
\draw[thick] (B) -- (-1.5,-0.5); 
\draw[thick] (C) -- (-1,-0.5);
\node at (-2,-0.75) {$a$}; 
\node at (-1.5,-0.75) {$b$}; 
\node at (-1,-0.75) {$c$}; 
\draw[thick] (-2,-1) -- (-2,-1.5); 
\draw[thick] (-1.5,-1) -- (-1.5,-1.5); 
\draw[thick] (-1,-1) -- (-1,-1.5);
\node at (-1.5,-2) {$\dist$};
\draw[thick] (-2.5,-2.5) -- (-2.5,-3); 
\draw[thick] (-2,-2.5) -- (-2,-3); 
\draw[green,densely dashed] (-2.25,-2.75) ellipse [x radius=0.4cm, y radius = 0.1cm]; 
\draw[thick] (-1,-2.5) -- (-1,-3); 
\draw[thick] (-0.5,-2.5) -- (-0.5,-3); 
\draw[green,densely dashed] (-0.75,-2.75) ellipse [x radius=0.4cm, y radius = 0.1cm]; 
\draw[thick,yellow] (-1,-2.75) arc[start angle=60, end angle=120, radius=1cm];
\end{tikzpicture}
\end{center}
% ((a + b) * c) ; dist <=> dist ; ((a * c) + (b * c))
% LHS: (t1 + t3) * t5 ~> (t2 + t4) * t6 ~> (t2 * t6) + (t4 * t6)
% RHS: (t1 + t3) * t5 ~> (t1 * t5) + (t3 * t5) ~> (t2 * t6) + (t4 * t6)

The constructs in Fig.~\ref{figh} \ldots 
\begin{center}
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8}]
\end{tikzpicture}
\end{center}

>>>>

@@

But why are these particular coherence laws? Are they all necessary?
Conversely are they, in some appropriate sense, sufficient? This is
the so-called \emph{coherence problem}. Mac Lane, in his farewell address
as President of the American Mathematical Society~\cite{MacLane1976} gives
a good introduction and overview of such problems.  A more modern
interpretation (which can nevertheless be read into Mac Lane's own
exposition) would read as follows: given a set of equalities on abstract
words, regarded as a rewrite system, and two means of rewriting a word
in that language to another, is there some suitable notion of canonical
form that expresses the essential uniqueness of the non-trivial 
rewrites?  Note how this word-and-rewrite problem is essentially
independent of the eventual interpretation. But one must take some care,
as there are obvious degenerate cases (involving ``trivial'' equations
involving $0$ or $1$) which lead to non-uniqueness. The landmark
results, first by Kelly-Mac Lane~\cite{KELLY197197} for closed
symmetric monoidal categories, then (independently) Laplaza and
Kelly~\cite{laplaza72,kelly74} for symmetric Rig Categories, is
that indeed there are sound and complete coherence conditions that
insure that all the ``obvious'' equalities between different abstract
words in these systems give rise to commutative diagrams. The
``obvious'' equalities come from \emph{syzygies} or
\emph{critical pairs} of the system of equations.

\begin{figure}[tb]
Let $c_1 : t_1 \leftrightarrow t_2$,  $c_2 : t_2 \leftrightarrow t_3$, and $c_3 : t_3 \leftrightarrow t_4$:
\[\def\arraystretch{1.3}
\begin{array}{c}
  {c_1 \odot (c_2 \odot c_3) \Leftrightarrow (c_1 \odot c_2) \odot c_3}
\\
  {(c_1 \oplus (c_2 \oplus c_3)) \odot \assoclp \Leftrightarrow \assoclp \odot ((c_1 \oplus c_2) \oplus c_3)}
\\
  {(c_1 \otimes (c_2 \otimes c_3)) \odot \assoclt \Leftrightarrow \assoclt \odot ((c_1 \otimes c_2) \otimes c_3)}
\\
  {((c_1 \oplus c_2) \oplus c_3) \odot \assocrp \Leftrightarrow \assocrp \odot (c_1 \oplus (c_2 \oplus c_3))}
\\
  {((c_1 \otimes c_2) \otimes c_3) \odot \assocrt \Leftrightarrow \assocrt \odot (c_1 \otimes (c_2 \otimes c_3))}
\\
  {\assocrp \odot \assocrp \Leftrightarrow ((\assocrp \oplus \idc) \odot \assocrp) \odot (\idc \oplus \assocrp)}
\\
  {\assocrt \odot \assocrt \Leftrightarrow ((\assocrt \otimes \idc) \odot \assocrt) \odot (\idc \otimes \assocrt)}
\end{array}\]
\caption{\label{figj}Signatures of level-2 $\Pi$-combinators: associativity}
\end{figure}

Conveniently, the various coherence conditions can be naturally
grouped into ``related'' laws.  Each group basically captures the
interactions between compositions of level-1 $\Pi$ combinators.

The constructs in Fig.~\ref{figj} capture the informal idea that all
the different ways of associating programs are equivalent. The first
says that sequential composition itself ($\odot$) is associative.
The next $4$ capture how
the $\oplus$ and $\otimes$ combinators ``commute'' with re-association.
In other words, it expresses the type-level associativity of $+$ is
properly reflected by the properties of $\oplus$.
The last two equivalences show how composition of associativity combinators
interact together. For example, the last equivalence captures the idea that the
program $\assocrt \odot \assocrt$ transforms an input of
type $((t_1 * t_2) * t_3) * t_4$ to an output of type
$t_1 * (t_2 * (t_3 * t_4))$ as follows:

\begin{center}
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8},baseline=(current bounding box.center)]
\node[above] (A) at (-2,0) {$t_1$}; 
\node[above] (B) at (-1.5,0) {$t_2$}; 
\node[above] (C) at (-1,0) {$t_3$}; 
\node[above] (D) at (-0.5,0) {$t_4$}; 
\draw[thick] (A) -- (-2,-1.5); 
\draw[thick] (B) -- (-1.5,-1.5); 
\draw[thick] (C) -- (-1,-1.5);; 
\draw[thick] (D) -- (-0.5,-1.5); 
\draw[red,densely dashed] (-1.75,-0.75) ellipse [x radius=0.4cm, y radius = 0.1cm];
\draw[green,densely dashed] (-1.6,-0.75) ellipse [x radius=0.85cm, y radius = 0.2cm];
\end{tikzpicture}
$\leadsto$ 
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8},baseline=(current bounding box.center)]
\node[above] (A) at (-2,0) {$t_1$}; 
\node[above] (B) at (-1.5,0) {$t_2$}; 
\node[above] (C) at (-1,0) {$t_3$}; 
\node[above] (D) at (-0.5,0) {$t_4$}; 
\draw[thick] (A) -- (-2,-1.5); 
\draw[thick] (B) -- (-1.5,-1.5); 
\draw[thick] (C) -- (-1,-1.5);; 
\draw[thick] (D) -- (-0.5,-1.5); 
\draw[red,densely dashed] (-1.75,-0.75) ellipse [x radius=0.4cm, y radius = 0.1cm];
\draw[green,densely dashed] (-0.75,-0.75) ellipse [x radius=0.4cm, y radius = 0.1cm];
\end{tikzpicture}
$\leadsto$
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8},baseline=(current bounding box.center)]
\node[above] (A) at (-2,0) {$t_1$}; 
\node[above] (B) at (-1.5,0) {$t_2$}; 
\node[above] (C) at (-1,0) {$t_3$}; 
\node[above] (D) at (-0.5,0) {$t_4$}; 
\draw[thick] (A) -- (-2,-1.5); 
\draw[thick] (B) -- (-1.5,-1.5); 
\draw[thick] (C) -- (-1,-1.5);; 
\draw[thick] (D) -- (-0.5,-1.5); 
\draw[red,densely dashed] (-0.9,-0.75) ellipse [x radius=0.85cm, y radius = 0.2cm];
\draw[green,densely dashed] (-0.75,-0.75) ellipse [x radius=0.4cm, y radius = 0.1cm];
\end{tikzpicture}
\end{center}
% \[ 
% ((t_1 * t_2) * t_3) * t_4 \leadsto
% (t_1 * t_2) * (t_3 * t_4) \leadsto
% t_1 * (t_2 * (t_3 * t_4))
% \]

\begin{center}
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8},baseline=(current bounding box.center)]]
\node[above] (A) at (-2,0) {$t_1$}; 
\node[above] (B) at (-1.5,0) {$t_2$}; 
\node[above] (C) at (-1,0) {$t_3$}; 
\node[above] (D) at (-0.5,0) {$t_4$}; 
\draw[thick] (A) -- (-2,-1.5); 
\draw[thick] (B) -- (-1.5,-1.5); 
\draw[thick] (C) -- (-1,-1.5);; 
\draw[thick] (D) -- (-0.5,-1.5); 
\draw[red,densely dashed] (-1.75,-0.75) ellipse [x radius=0.4cm, y radius = 0.1cm];
\draw[green,densely dashed] (-1.6,-0.75) ellipse [x radius=0.85cm, y radius = 0.2cm];
\end{tikzpicture}
$\leadsto$ 
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8},baseline=(current bounding box.center)]]
\node[above] (A) at (-2,0) {$t_1$}; 
\node[above] (B) at (-1.5,0) {$t_2$}; 
\node[above] (C) at (-1,0) {$t_3$}; 
\node[above] (D) at (-0.5,0) {$t_4$}; 
\draw[thick] (A) -- (-2,-1.5); 
\draw[thick] (B) -- (-1.5,-1.5); 
\draw[thick] (C) -- (-1,-1.5);; 
\draw[thick] (D) -- (-0.5,-1.5); 
\draw[red,densely dashed] (-1.25,-0.75) ellipse [x radius=0.4cm, y radius = 0.1cm];
\draw[green,densely dashed] (-1.5,-0.75) ellipse [x radius=0.85cm, y radius = 0.2cm];
\end{tikzpicture}
$\leadsto$
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8},baseline=(current bounding box.center)]]
\node[above] (A) at (-2,0) {$t_1$}; 
\node[above] (B) at (-1.5,0) {$t_2$}; 
\node[above] (C) at (-1,0) {$t_3$}; 
\node[above] (D) at (-0.5,0) {$t_4$}; 
\draw[thick] (A) -- (-2,-1.5); 
\draw[thick] (B) -- (-1.5,-1.5); 
\draw[thick] (C) -- (-1,-1.5);; 
\draw[thick] (D) -- (-0.5,-1.5); 
\draw[red,densely dashed] (-1.25,-0.75) ellipse [x radius=0.4cm, y radius = 0.1cm];
\draw[green,densely dashed] (-1.0,-0.75) ellipse [x radius=0.85cm, y radius = 0.2cm];
\end{tikzpicture}
$\leadsto$
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8},baseline=(current bounding box.center)]]
\node[above] (A) at (-2,0) {$t_1$}; 
\node[above] (B) at (-1.5,0) {$t_2$}; 
\node[above] (C) at (-1,0) {$t_3$}; 
\node[above] (D) at (-0.5,0) {$t_4$}; 
\draw[thick] (A) -- (-2,-1.5); 
\draw[thick] (B) -- (-1.5,-1.5); 
\draw[thick] (C) -- (-1,-1.5);; 
\draw[thick] (D) -- (-0.5,-1.5); 
\draw[green,densely dashed] (-0.9,-0.75) ellipse [x radius=0.85cm, y radius = 0.2cm];
\draw[red,densely dashed] (-0.75,-0.75) ellipse [x radius=0.4cm, y radius = 0.1cm];
\end{tikzpicture}
\end{center}
% \[
% ((t_1 * t_2) * t_3) * t_4 \leadsto
% (t_1 * (t_2 * t_3)) * t_4 \leadsto
% t_1 * ((t_2 * t_3) * t_4) \leadsto
% t_1 * (t_2 * (t_3 * t_4))
% \]

\noindent This of course gives rise to a \emph{critical pair} in words over the
level-1 language, as both of these programs are between the same types.
Since neither of these involve either trivial types (like $0$ or $1$) nor
twists (i.e. automorphisms) on the types themselves, coherence requires that
these in fact be equivalent programs.  One interpretation is that
\emph{outermost} re-associations is the same as \emph{innermost}
re-associations.

\jc{I am not a big fan of these pictures -- mainly because I can't give any
intuition based on them of why these can be smoothly deformed into one another.
All the ``pictures'' I can come up with [via purely formal reasoning] sit in at least
5 dimensions -- one for each of the wires, and another to give room to maneuver.}

@@

The constructs in Fig.~\ref{figi} are the basic coherence for
$\dist$, $\distl$, $\factor$ and $\factorl$: the type-level distribution
and factoring has to commute with the combinator-level $\oplus$ and $\otimes$.

\begin{comment}
\begin{center}
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8}]
\node[above] (A) at (-2,0) {$t_1$}; 
\node[above] (B) at (-1.5,0) {$t_3$}; 
\node[above] (C) at (-1,0) {$t_5$}; 
\draw[thick,yellow] (-1.5,-0.25) arc[start angle=60, end angle=120, radius=0.5cm];
\draw[thick] (A) -- (-2,-0.5); 
\draw[thick] (B) -- (-1.5,-0.5); 
\draw[thick] (C) -- (-1,-0.5);
\node at (-2,-0.75) {$a$}; 
\node at (-1.5,-0.75) {$b$}; 
\node at (-1,-0.75) {$c$}; 
\draw[thick] (-2,-1) -- (-2,-1.5); 
\draw[thick] (-1.5,-1) -- (-1.5,-1.5); 
\draw[thick] (-1,-1) -- (-1,-1.5);
\node at (-1.5,-2) {$\dist$};
\draw[thick] (-2.5,-2.5) -- (-2.5,-3); 
\draw[thick] (-2,-2.5) -- (-2,-3); 
\draw[green,densely dashed] (-2.25,-2.75) ellipse [x radius=0.4cm, y radius = 0.1cm]; 
\draw[thick] (-1,-2.5) -- (-1,-3); 
\draw[thick] (-0.5,-2.5) -- (-0.5,-3); 
\draw[green,densely dashed] (-0.75,-2.75) ellipse [x radius=0.4cm, y radius = 0.1cm]; 
\draw[thick,yellow] (-1,-2.75) arc[start angle=60, end angle=120, radius=1cm];
\end{tikzpicture}
\end{center}
% ((a + b) * c) ; dist <=> dist ; ((a * c) + (b * c))
% LHS: (t1 + t3) * t5 ~> (t2 + t4) * t6 ~> (t2 * t6) + (t4 * t6)
% RHS: (t1 + t3) * t5 ~> (t1 * t5) + (t3 * t5) ~> (t2 * t6) + (t4 * t6)
\end{comment}

@@

The constructs in Fig.~\ref{figh} express various properties of composition.
The first two says that $\idc$ is a left and right identity for sequential composition.

\begin{center}
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8}]
\end{tikzpicture}
\end{center}

@@
